---
title: "Space Flight Sentiment"
subtitle: "Draft Analysis"
date: "Updated: `r format(Sys.Date(), format='%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
---

---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.retina = 4, out.width = "100%")
```


```{r message=FALSE, warning=FALSE, fig.retina=4}
# Libraries
pacman::p_load(tidyverse, countrycode, sf, state, htmltools, htmlwidgets, urltools, janitor, DT, RColorBrewer, plotly, ussf, arrow, hrbrthemes, overlapping, sentimentr, knitr, kableExtra, estimatr, texreg)
```


```{r, include = FALSE}
serp_locations <-
  read_csv(here::here("data/locations_serp_google_2021_11_09.csv")) %>%
  filter(country_iso_code == "US", location_type == "County") %>%
  mutate(
    location_name = str_replace(location_name, " Borough", ""),
    location_name = str_replace(location_name, " Census Area", ""),
    location_name = str_replace(location_name, " Municipality", ""),
    location_name = str_replace(location_name, " City and", "")
  )

county_maps <- 
  ussf::boundaries(geography = "county") %>% 
  rename(county_fips = GEOID) %>% 
  left_join(read_csv(here::here("data/uscounties.csv")), by = "county_fips") %>%
  mutate(
    location_name = str_c(county_full, state_name, "United States", sep = ","),
    location_name = str_replace(location_name, " Borough", ""),
    location_name = str_replace(location_name, " Census Area", ""),
    location_name = str_replace(location_name, " Municipality", ""),
    location_name = str_replace(location_name, " City and", ""),
    location_name = if_else(
      location_name == "LaSalle Parish,Louisiana,United States", "La Salle Parish,Louisiana,United States", location_name
    ),
    location_name = if_else(
      location_name == "Doña Ana County,New Mexico,United States", "Dona Ana County,New Mexico,United States", location_name
    )
  ) %>% 
  left_join(serp_locations, by = "location_name")

df_bezos <- read_parquet(here::here("data/for_seth_bezos.parquet")) %>% rename(location_code = location)
df_musk <- read_parquet(here::here("data/for_seth_musk.parquet")) %>% rename(location_code = location)
df_branson <- read_parquet(here::here("data/for_seth_branson.parquet")) %>% rename(location_code = location)

df <- 
  bind_rows("Bezos" = df_bezos, "Musk" = df_musk, "Branson" = df_branson, .id = "id") %>% 
  left_join(county_maps, by = "location_code") %>%
  select(id, query, county = county_full, county_fips, search_rank = rank_group, domain, title, description, url, language, sentiment) %>%
  arrange(query, county, search_rank)

df <- bind_cols(df, read_csv(here::here("data/space_flight_sentimentr.csv"))) # check sorting before merge!

df_openintro <-
  read_csv(here::here("data/us_county_openintro.csv")) %>% 
  clean_names() %>% 
  remove_empty() %>% 
  rename(county_fips = fips) %>% 
  mutate(
    county_fips = county_fips %>% as.character(),
    county_fips = if_else(str_length(county_fips) == 4, str_c("0", county_fips), county_fips)
  )

df <- df %>% left_join(df_openintro, by = "county_fips")

# df %>% distinct(county_fips) %>% anti_join(df_openintro)

rm(df_bezos, df_musk, df_branson, county_maps, serp_locations, df_openintro)
gc()

df %>% glimpse()
```

```{r, eval=F}
# extract data for seth
# bind_rows(df_bezos, df_branson, df_musk) %>%
#   select(query, rank_group, domain, title, description, url, location_code, language, sentiment) %>% 
#   left_join(county_maps, by = "location_code") %>% 
#   select(query, county = county_full, search_rank = rank_group, domain, title, description, url, language, sentiment_bert = sentiment) %>%
#   arrange(query, county, search_rank) %>% 
#   write_csv(here::here("data/space_flight_raw_data_v1.csv"))
```


```{r, eval=F}
# df_sentiment <-
#   df %>% 
#   transmute(
#     text = str_c(title, description, sep = ". ") %>% str_squish()
#   ) %>% 
#   pull(text) %>% 
#   get_sentences() %>% 
#   sentiment_by()
# 
# df_sentiment %>% glimpse()
# df_sentiment %>% write_csv(here::here("data/space_flight_sentimentr.csv"))

```


```{r, eval=F}
df_domains <-
  read_csv(here::here("data/space_flights/space_flight_raw_data_v1.csv")) %>% 
  mutate(
    domain = str_replace(domain, "^www.", "")
  ) %>%
  count(domain) %>% arrange(-n)

df_mbias <- read_csv(here::here("data/space_flights/media-bias-scrubbed-results.csv"))

bind_cols(
    df_mbias,
    df_mbias %>% pull(url) %>% domain() %>% tld_extract()
  ) %>% 
  transmute(
    domain = str_replace(domain, "^www.", ""),
    bias_rating
  ) %>%
  left_join(df_domains, ., by = "domain") %>% 
  distinct(domain, .keep_all = T) %>% 
  arrange(-n) %>% 
  left_join(read_csv(here::here("data/space_flights/media-bias-rankings.csv")), by="bias_rating") %>% 
  mutate(bias_label = str_extract(bias_label, "[a-z]+" )) %>% 
  mutate(
    bias_label = case_when(
      bias_label == "leastbiased" ~ "N",
      bias_label == "left" ~ "L",
      bias_label == "leftcenter" ~ "LC",
      bias_label == "right" ~ "R",
      bias_label == "rightcenter" ~ "RC",
      TRUE ~ NA_character_
    )
  ) %>% 
  select(domain, n, bias_label, bias_rating) %>% count(bias_label)
  #writexl::write_xlsx(here::here("data/space_flights/space_flight_data_domains_v2.xlsx"))
```



<br/>

## Descriptives

### Sentiment distribution by capitalist

Sentiment polarity calculation details [here](https://github.com/trinker/sentimentr#the-equation).

```{r}
df %>% 
  ggplot(aes(ave_sentiment)) + 
  geom_histogram(alpha = 0.9) + 
  facet_wrap(vars(id)) +
  theme_ipsum() +
  labs(
    x = "Sentiment",
    y = "Search result count"
  )
```


---

<br/>

### Who does best{.tabset}

#### Unweighted means

##### Top result

```{r}
df %>% 
  filter(search_rank == 1) %>% 
  group_by(id) %>%
  summarize(
    mean_sentiment = mean(ave_sentiment, na.rm = T),
    sd_sentiment = sd(ave_sentiment, na.rm = T),
    n_results = n()
  ) %>% 
  arrange(-mean_sentiment) %>% 
  kable() %>% 
  kable_styling()
```

##### Top 10 results

```{r}
df %>% 
  filter(search_rank <= 10) %>% 
  group_by(id) %>%
  summarize(
    mean_sentiment = mean(ave_sentiment, na.rm = T),
    sd_sentiment = sd(ave_sentiment, na.rm = T),
    n_results = n()
  ) %>% 
  arrange(-mean_sentiment) %>% 
  kable() %>% 
  kable_styling()
```


##### Overall

```{r}
df %>% 
  group_by(id) %>%
  summarize(
    mean_sentiment = mean(ave_sentiment, na.rm = T),
    sd_sentiment = sd(ave_sentiment, na.rm = T),
    n_results = n()
  ) %>% 
  arrange(-mean_sentiment) %>% 
  kable() %>% 
  kable_styling()
```



#### Means weighted by $\frac{1}{search\_rank}$

##### Top result

```{r}
df %>% 
  filter(search_rank == 1) %>% 
  group_by(id) %>%
  summarize(
    mean_sentiment = weighted.mean(ave_sentiment, w = 1/search_rank, na.rm = T),
    sd_sentiment = sd(ave_sentiment, na.rm = T),
    n_results = n()
  ) %>% 
  arrange(-mean_sentiment) %>% 
  kable() %>% 
  kable_styling()
```

##### Top 10 results

```{r}
df %>% 
  filter(search_rank <= 10) %>% 
  group_by(id) %>%
  summarize(
    mean_sentiment = weighted.mean(ave_sentiment, w = 1/search_rank, na.rm = T),
    sd_sentiment = sd(ave_sentiment, na.rm = T),
    n_results = n()
  ) %>% 
  arrange(-mean_sentiment) %>% 
  kable() %>% 
  kable_styling()
```


##### Overall

```{r}
df %>% 
  group_by(id) %>%
  summarize(
    mean_sentiment = weighted.mean(ave_sentiment, w = 1/search_rank, na.rm = T),
    sd_sentiment = sd(ave_sentiment, na.rm = T),
    n_results = n()
  ) %>% 
  arrange(-mean_sentiment) %>% 
  kable() %>% 
  kable_styling()
```


---

<br/>


### Mean sentiment variation with search rank

```{r, out.width="100%", fig.retina=4}
df %>% 
  group_by(id, search_rank) %>%
  summarize(
    ave_sentiment = mean(ave_sentiment, na.rm = T),
    n_results = n(),
  ) %>%
  ungroup() %>% 
  ggplot(aes(search_rank, ave_sentiment)) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  geom_point(alpha = 0.75) +
  geom_smooth() +
  theme_ipsum() +
  facet_wrap(vars(id)) +
  labs(
    x = "Search rank",
    y = "Mean sentiment",
    color = ""
  )
```


---

<br/>

## County-level heterogeneity{.tabset}

County level data details [here](https://www.openintro.org/data/index.php?data=county_complete).

The loess curves below show very little spatial variation exists. The y-axis is weighted mean of sentiment at the county level (weight = $\frac{1}{search\_rank}$).

```{r}
df %>% 
  group_by(county_fips, id) %>% 
  summarize_at(
    vars(ave_sentiment, age_over_65_2019, female_2010, white_not_hispanic_2019, some_college_2017, per_capita_income_2019),
    ~ weighted.mean(., w = 1/search_rank, na.rm = T)
  ) %>% 
  ggplot(aes(age_over_65_2019, ave_sentiment, color=id)) +
  geom_smooth(method = "loess") +
  theme_ipsum() +
  theme(legend.position = "bottom") +
  labs(
    y = "County sentiment (weighted avg.)",
    color = ""
  )
```


```{r}
df %>% 
  group_by(county_fips, id) %>% 
  summarize_at(
    vars(ave_sentiment, age_over_65_2019, female_2010, white_not_hispanic_2019, some_college_2017, per_capita_income_2019),
    ~ weighted.mean(., w = 1/search_rank, na.rm = T)
  ) %>% 
  ggplot(aes(female_2010, ave_sentiment, color=id)) +
  geom_smooth(method = "loess") +
  theme_ipsum() +
  theme(legend.position = "bottom") +
  labs(
    y = "County sentiment (weighted avg.)",
    color = ""
  )
```


```{r}
df %>% 
  group_by(county_fips, id) %>% 
  summarize_at(
    vars(ave_sentiment, age_over_65_2019, female_2010, white_not_hispanic_2019, some_college_2017, per_capita_income_2019),
    ~ weighted.mean(., w = 1/search_rank, na.rm = T)
  ) %>% 
  ggplot(aes(white_not_hispanic_2019, ave_sentiment, color=id)) +
  geom_smooth(method = "loess") +
  theme_ipsum() +
  theme(legend.position = "bottom") +
  labs(
    y = "County sentiment (weighted avg.)",
    color = ""
  )
```



```{r}
df %>% 
  group_by(county_fips, id) %>% 
  summarize_at(
    vars(ave_sentiment, age_over_65_2019, female_2010, white_not_hispanic_2019, some_college_2017, per_capita_income_2019),
    ~ weighted.mean(., w = 1/search_rank, na.rm = T)
  ) %>% 
  ggplot(aes(some_college_2017, ave_sentiment, color=id)) +
  geom_smooth(method = "loess") +
  theme_ipsum() +
  theme(legend.position = "bottom") +
  labs(
    y = "County sentiment (weighted avg.)",
    color = ""
  )
```


```{r}
df %>% 
  group_by(county_fips, id) %>% 
  summarize_at(
    vars(ave_sentiment, age_over_65_2019, female_2010, white_not_hispanic_2019, some_college_2017, per_capita_income_2019),
    ~ weighted.mean(., w = 1/search_rank, na.rm = T)
  ) %>% 
  ggplot(aes(per_capita_income_2019, ave_sentiment, color=id)) +
  geom_smooth(method = "loess") +
  theme_ipsum() +
  theme(legend.position = "bottom") +
  labs(
    y = "County sentiment (weighted avg.)",
    color = ""
  )
```
































<!-- ## Mean sentiment across _all_ search results {.tabset} -->

<!-- ### Bezos -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Bezos") %>%  -->
<!--   group_by(location_code) %>%  -->
<!--   summarize(sentiment = mean(sentiment, na.rm = TRUE)) %>%  -->
<!--   left_join(county_maps, ., by = "location_code") %>%  -->
<!--   mutate( -->
<!--     hover_text = str_c(county_full, sentiment, sep = "\n") -->
<!--   ) %>%  -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = sentiment))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Greens"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Mean sentiment (All)") -->
<!-- ``` -->


<!-- ### Branson -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Branson") %>%  -->
<!--   group_by(location_code) %>%  -->
<!--   summarize(sentiment = mean(sentiment, na.rm = TRUE)) %>%  -->
<!--   left_join(county_maps, ., by = "location_code") %>%  -->
<!--   mutate( -->
<!--     hover_text = str_c(county_full, sentiment, sep = "\n") -->
<!--   ) %>%  -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = sentiment))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Greens"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Mean sentiment (All)") -->
<!-- ``` -->


<!-- ### Musk -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Musk") %>% -->
<!--   group_by(location_code) %>%  -->
<!--   summarize(sentiment = mean(sentiment, na.rm = TRUE)) %>%  -->
<!--   left_join(county_maps, ., by = "location_code") %>%  -->
<!--   mutate( -->
<!--     hover_text = str_c(county_full, sentiment, sep = "\n") -->
<!--   ) %>%  -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = sentiment))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Greens"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Mean sentiment (All)") -->
<!-- ``` -->


<!-- <br/><br/> -->

<!-- ## Mean sentiment across _top 10_ search results {.tabset} -->

<!-- ### Bezos -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Bezos") %>% -->
<!--   group_by(location_code) %>%  -->
<!--   slice(1:10) %>%  -->
<!--   summarize(sentiment = mean(sentiment, na.rm = TRUE)) %>%  -->
<!--   left_join(county_maps, ., by = "location_code") %>%  -->
<!--   mutate( -->
<!--     hover_text = str_c(county_full, sentiment, sep = "\n") -->
<!--   ) %>%  -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = sentiment))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Greens"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Mean sentiment (top 10)") -->
<!-- ``` -->


<!-- ### Branson -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Branson") %>% -->
<!--   group_by(location_code) %>%  -->
<!--   slice(1:10) %>%  -->
<!--   summarize(sentiment = mean(sentiment, na.rm = TRUE)) %>%  -->
<!--   left_join(county_maps, ., by = "location_code") %>%  -->
<!--   mutate( -->
<!--     hover_text = str_c(county_full, sentiment, sep = "\n") -->
<!--   ) %>%  -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = sentiment))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Greens"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Mean sentiment (top 10)") -->
<!-- ``` -->


<!-- ### Musk -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Musk") %>% -->
<!--   group_by(location_code) %>%  -->
<!--   slice(1:10) %>%  -->
<!--   summarize(sentiment = mean(sentiment, na.rm = TRUE)) %>%  -->
<!--   left_join(county_maps, ., by = "location_code") %>%  -->
<!--   mutate( -->
<!--     hover_text = str_c(county_full, sentiment, sep = "\n") -->
<!--   ) %>%  -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = sentiment))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Greens"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Mean sentiment (top 10)") -->
<!-- ``` -->



<!-- <br/><br/> -->

<!-- ## Distribution overlap in _top 10_ vs _all_ search results{.tabset} -->

<!-- For any county, a high value here indicates that the sentiment distribution of top 10 results overlaps well with the sentiment distribution of all search results (i.e. high information _visibility_). -->

<!-- ### Bezos -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Bezos") %>% -->
<!--   group_by(location_code) %>% -->
<!--   summarize(overlap = overlap(list(sentiment, sentiment %>% head(10)))$OV) %>% -->
<!--   left_join(county_maps, ., by = "location_code") %>% -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = overlap))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Blues"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Overlap (All vs top 10)") -->
<!-- ``` -->


<!-- ### Branson -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Branson") %>% -->
<!--   group_by(location_code) %>% -->
<!--   summarize(overlap = overlap(list(sentiment, sentiment %>% head(10)))$OV) %>% -->
<!--   left_join(county_maps, ., by = "location_code") %>% -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = overlap))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Blues"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Overlap (All vs top 10)") -->
<!-- ``` -->


<!-- ### Musk -->

<!-- ```{r, out.width="100%", fig.retina=4} -->
<!-- df %>% -->
<!--   filter(id == "Musk") %>% -->
<!--   group_by(location_code) %>% -->
<!--   summarize(overlap = overlap(list(sentiment, sentiment %>% head(10)))$OV) %>% -->
<!--   left_join(county_maps, ., by = "location_code") %>% -->
<!--   ggplot() + -->
<!--   geom_sf(aes(fill = overlap))  + -->
<!--   scale_fill_gradientn( -->
<!--     colors = RColorBrewer::brewer.pal(n = 9, name = "Blues"), -->
<!--   ) + -->
<!--   theme_void() + -->
<!--   theme(legend.key.width = unit(1, 'cm'), legend.position = "bottom") + -->
<!--   labs(fill = "Overlap (All vs top 10)") -->
<!-- ``` -->






